---
title: "Basic Webscraping"
---

<style type="text/css">
.table {

    width: 80%;
    margin-left:10%; 
    margin-right:10%;
}
</style>
```{r,setup, echo=FALSE, cache=TRUE}
## numbers >= 10^5 will be denoted in scientific notation,
## and rounded to 2 digits
options(scipen = 3, digits = 3)
```



## Exercises

1. Read the HTML content of the following URL with a variable called webpage: https://money.cnn.com/data/us_markets/ At this point, it will also be useful to open this web page in your browser.
```{r}
#After installing the 'rvest' package, we can use the read_html function on the the given url to save the content of the URL.

library(rvest)
url <- "https://money.cnn.com/data/us_markets/"
webpage <- read_html(url)
```
2. Get the session details (status, type, size) of the above mentioned URL.
```{r}
#Running the html_session function on the given URL will give the session details.
html_session(url)
```
3. Extract all of the sector names from the “Stock Sectors” table (bottom left of the web page.)
```{r}
#Running html_nodes on the webpage and specifying table and then running html_table on the nodes gives data frames containing the data on the webpage. 
tables <- html_table(html_nodes(webpage, "table"))
#Three tables are then saved from the page. The second table is the "Stock Sectors" table, so we can then select that one.
Stock_Sectors <- tables[[2]]
#The first column of the Stock_Sectors table contains the names.
Stock_Sectors[,1]
```
4. Extract all of the “3 Month % Change” values from the “Stock Sectors” table.
```{r}
#The second column of the Stock_Sectors table contains the "3 Month % Change" values.
Stock_Sectors[,2]
```
5. Extract the table “What’s Moving” (top middle of the web page) into a data-frame.
```{r}
#We saved the "What's Moving" table in the "table" list of data frames above. It is the first table in the list.
Whats_Moving <- tables[[1]]
Whats_Moving
```
6. Re-construct all of the links from the first column of the “What’s Moving” table.
Hint: the base URL is “https://money.cnn.com”
```{r}
#I used the selectorgadget to pick out the appropriate CSS selector - in this case it is "tr .wsod_symbol" - and the "href" attribute combined with the base URL recreates the links.
url_suffixes <- html_attr(html_nodes(webpage, css = "tr .wsod_symbol"), "href")
paste("https://money.cnn.com", url_suffixes, sep = "")
```
7. Extract the titles under the “Latest News” section (bottom middle of the web page.)
```{r}
#This bit of code extracts the nodes from the "Latest News" section, and the html_text function extracts the titles.
html_text(html_nodes(webpage, css = ".HeadlineList a"))
```
8. To understand the structure of the data in a web page, it is often useful to know what the underlying attributes are of the text you see.
Extract the attributes (and their values) of the HTML element that holds the timestamp underneath the “What’s Moving” table.
```{r}
#The html_attrs function gives the attributes of the HTML element, which is selected using the SelectorGadget app to find the appropriate css selector.
html_attrs(html_node(webpage, css = ".wsod_disclaimer span"))

```
9. Extract the values of the blue percentage-bars from the “Trending Tickers” table (bottom right of the web page.)
Hint: in this case, the values are stored under the “class” attribute.
```{r}
#This time, we want the class attribute of the values that are given after selecting for ".bars" (found using SelectorGadget). This returns a vector of strings with values "bars pctX" where X is the percentage value of the bar. Then the "bars pct" is removed to give just a vector of the values.
values <- html_attr(html_nodes(webpage, ".bars"), "class")
as.numeric(gsub("bars pct", "", values))
```
10. Get the links of all of the “svg” images on the web page.

```{r}
#We use html_nodes to select the images, the html_attr function collects the url extensions of the images. Then the images that have a .svg file type are selected, and their urls are collected.
images <- html_attr(html_nodes(webpage, "img"), "src")
svg_images <- images[grep("svg", images)]
paste("https://money.cnn.com", svg_images, sep = "")
```